\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsfonts}
\usepackage{amssymb,amsthm}
\usepackage{kpfonts}
\usepackage[left=2cm, right=2cm, top=2cm, bottom=2cm]{geometry}

\newcommand{\Z}{\mathbb Z}
\newcommand{\N}{\mathbb N}
\newcommand{\Q}{\mathbb Q}
\newcommand{\R}{\mathbb R}
\newcommand{\C}{\mathbb C}

\renewcommand{\leq}{\leqslant}
\renewcommand{\geq}{\geqslant}
\renewcommand{\ge}{\geqslant}
\renewcommand{\le}{\leqslant}

%Define theorems
\theoremstyle{definition}
\newtheorem{problem}{Problem}
\newcounter{punkt}[problem]
\newcommand{\pp}{\,\noindent\addtocounter{punkt}{1}$\alph{punkt})$\,}
\newcommand{\ppp}{\,\noindent\addtocounter{punkt}{1}$\alph{punkt}^*$)\,}

\newenvironment{solution}
{\renewcommand\qedsymbol{$\blacksquare$}\begin{proof}[Solution.]}
	{\end{proof}}

\setlength\parindent{0pt}
\setlength{\parskip}{5pt}

%define header
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\rhead{Fall 2020}
\lhead{Yury Ustinovskiy}
\chead{Algebra MATH-UA.0343-003}

\begin{document}
	
	\begin{center}
		\Large{\textbf{Homework 1}}
	\end{center}
	
	
	\textbf{Due:} Wednesday, September 16
	
	{\footnotesize Each problem is worth 10 points. To get the full credit, write complete, detailed solutions. You may use any of the results from the class without a proof, but you have to state them explicitly.}
	
	\begin{problem} Let $f:\R\to \R$ be the map $f:x\mapsto (x+1)^2$. Compute the inverse image sets $f^{-1}(A)$ of the following sets $A$:
		
		\pp $\{-9\}$,
		
		\pp $\{-1,0,4\}$,
		
		\pp $[0,+\infty) = \{x\in \R:\ x\geq 0\}$.
	\end{problem}
	
	%Copy the \begin{solution}-\end{solution} block below to type your solutions to other problems
	\begin{solution}
		Type your solution here
	\end{solution}
	
	
	\begin{problem}
		Let $f\colon X\to Y$ be a map, and consider $A_1,A_2\subset X$.
		
		\pp Prove that $f(A_1\cup A_2)=f(A_1)\cup f(A_2)$.
		
		\pp Prove that $f(A_1\cap A_2)\subset f(A_1)\cap f(A_2)$ and give an example in which equality fails.
	\end{problem}
	
	\begin{problem}
		Suppose that $S = \{1, 2, 3\}$. Define a map $\pi\colon S \to S$ by
		\[
		\begin{split}
		\pi(1) = 2,\\
		\pi(2) = 3,\\
		\pi(3) = 1.
		\end{split}
		\]
		\pp Find the images of elements of $S$ under the maps $(\pi\circ \pi)$ and $(\pi\circ \pi\circ \pi)$.
		
		\pp Is $\pi$ surjective? injective?. If it is bijective, find $\pi^{-1}$.
	\end{problem}
	
	\begin{problem}
		Let $f\colon X\to Y$ and $g\colon Y\to Z$ be maps between sets. Prove that
		
		\pp If $g\circ f$ is injective, then $f$ is injective;
		
		\pp If $g\circ f$ is surjective then $g$ is surjective.
	\end{problem}
	
	\begin{problem}
		Let $f \colon A \to B$ and $g \colon B \to C$ be invertible mappings; that is, mappings such that $f^{-1}$ and $g^{-1}$ exist. Show that $(g \circ f)^{-1} = f^{-1}\circ g^{-1}$.
	\end{problem}
	
\end{document}